Probing the inner kpc of massive galaxies with strong gravitational lensing

### 2014-11-05 ms.tex
modifying everything

The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.][]{Wallington:93, Evans:02, Keeton:03}. These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}. 
Observational searches for these images have found a number of candidates \citep[e.g.][]{}. Although observations
of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:05}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}. To avoid the possibility of absorption in the lens, most searches have focused on lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies.

>>>>

The individual behavior and statistical properties of central images in lensed populations have been extensively studied \citep[e.g.][]{Wallington:93, Evans:02, Keeton:03}. These studies show that central images could have a wide range of magnifications \citep[e.g.,][]{Keeton:03}. 
Observational searches for these images have found a number of candidates. Although observations
of central images in group and cluster lenses are not uncommon \citep[e.g.,][]{Inada:08}, only one secure detections of a central image of a galaxy-scale lens exists to date \citep{Winn:04}. To avoid the possibility of absorption in the lens, most searches have focused on lensed radio quasars and the radio spectrum of candidate central images have been used to distinguish them from potential faint emission from the lens galaxies \citep[e.g.,][]{Zhang:07}.
